Hunting experience shapes individual foraging specialization and predator-prey interactions in an online videogame

### 2023-05-16 manuscript/Chapter2-manuscript.Rmd
new MS version complete

Keywords: foraging behaviour, reciprocal behavioural plasticity, learning, antipredator behaviour, virtual ecology

@@

# Open percentages table
path <- file.path(here::here("outputs", "03_outputs_model-processing"))
percent_tab <- data.table(readRDS(file.path(path, "GAMM_percentages.rds")))

Out of all five models, the two that best predicted the data, with very similar expected log pointwise densities (elpd), were the models accounting for the prey group's speed (Table 1). Predators differed substantially in the relationship between hunting success and cumulative experience (i.e. expertise: Figure 1A-B). We found evidence that these differences were in part mediated by prey speed because individuals had distinct patterns after we controlled for the mean speed of the prey groups compared to when we did not (Figure 1A-B). For instance, many individual curves shifted upwards. Precisely, the percentage of individuals that displayed a >0.5 increase in success changed from `r toString(scales::percent(percent_tab[2,]$percentage, accuracy = 0.1))` to `r toString(scales::percent(percent_tab[5,]$percentage, accuracy = 0.1))` after we accounted for prey speed (Appendix S1: Figure S1A). In this model (i.e. Figure 1B-C), `r toString(scales::percent(percent_tab[4,]$percentage, accuracy = 0.1))` of the population showed a >0.5 decrease in success (Appendix S1: Figure S1B), and the remaining `r toString(scales::percent(percent_tab[6,]$percentage, accuracy = 0.1))` displayed little to no change (between -0.5 and 0.5) in success across experience (Appendix S1: Figure S1C).

@@

Individual predators differed slightly in their average movement speed across experience levels (i.e. predator ID (mean); Figure 2 and Appendix S1: Table S2). However, there was strong evidence that they displayed differences in foraging specialization, with a 0.1 unit increase in standard deviation from novice to advanced, indicating that differences increased slightly (i.e. predator ID (sigma) is higher at the advanced level; Figure 2 and Appendix S1: Table S2). Moreover, some individual predators switched from a flexible to a specialized hunting tactic, and vice-versa, as they gained experience (Figure 3). Importantly, 12.6% of the predator population displayed a large change in foraging specialization/flexibility with experience (i.e. >0.2 change in standard deviation), 44.7% displayed lower changes (i.e. >0.05 and <0.2 change in standard deviation), while 42.7% remained relatively stable (i.e. <0.05 change in standard deviation).

@@

The predator's mean speed and IIV were only weakly negatively correlated with hunting success across experience (Figure 4 and Appendix S4: Table S1), suggesting that slower/flexible and faster/specialist predators were both equally successful. However, there was strong evidence that individuals who encountered groups of prey with faster speeds were less successful (Figure 4A-B and Appendix S4: Table S1). Predators also had greater success across the study when encountering more variable groups of prey (Figure 4A-B and Appendix S4: Table S1). Both relationships remained structurally stable across experience (Figure 4-C)

@@

Hunting experience is predicted to increase predator foraging specialization when resources are predictable [@Estes.etal2003;@Tinker.etal2008;@Tinker.etal2009]. However, when resources vary, others predict that learning with experience should increase behavioural flexibility [@Stephens1993;@Ishii.Shimada2010;@Mery.Burns2010;@Snell-Rood2013;@Wright.etal2022]. Our results show that there was no directional increase in either behavioural specialization or flexibility with experience at the population level. Instead, individual predators developed their own expertise and behavioural trajectory over successive encounters with prey; there was a continuum of hunting styles ranging from a slower and flexible strategy to a highly specialized fast-paced strategy. Specialized cursorial hunters encountered similar groups of prey while slower and flexible hunters encountered varying groups of prey, with both achieving similar success over the study period. With experience, predators increasingly matched their foraging specialization to the speed of the prey that they encountered, but they did not achieve greater success, probably because the prey were also matching their speed to the predator. Our observations suggest that predators in *DBD* learn to adjust foraging specialization to the behaviour of the prey that they encounter throughout their lifetime in the game.

@@

Empirical research shows that task proficiency often increases nonlinearly with experience and stabilizes at an expert level [reviewed in @Dukas2019]. Our analyses revealed a similar trend, with a 13% population increase in success with experience. However, as we mentioned before, the matchmaking pairs players using a rank-based system, and the increase in expertise could have been even greater if predators were not paired with prey of similar skill. Individual predators in *DBD* also displayed distinct patterns of expertise acquisition. We predicted that this would occur if, by chance, predators differed in the prey that they encountered, because some may be easier and others more difficult to capture. In nature, prey can use a variety of defenses such as physical armaments, toxins, camouflage, or antipredator behaviours to escape predation [@BrodieIII.BrodieJr.1999;@Bowen.etal2002;@brodieCoEvolutionPredatorsPrey2010;@Nomura.etal2011;@Carey.Wahl2011]. In *DBD* we previously showed that faster movement is an effective strategy used by the prey to avoid predation [@FraserFranco.etal2022], and other studies have found that as well [@Walker.etal2005;@Kelley.Magurran2011;@Martin.etal2022]. Our results confirm that prey speed influenced expertise acquisition at the individual level to some extent. This is not surprising because capturing faster prey requires costly and specialized cognitive abilities and coordination [@Kelley.Magurran2011]. However, even if we accounted for prey speed, there were still important differences in expertise acquisition, which suggests that other antipredator tactics may also be involved.

For example, two well known antipredator tactics known to confuse human and non-human predators during the attack sequence are unpredictable escapes and turning angles [@Jones.etal2011;@Herbert-Read.etal2017;@Moore.etal2017;@Richardson.etal2018]. Yet, even if predators can adjust to unpredictable prey escapes [@Szopa-Comley.Ioannou2022], it could still be arduous for an individual to learn and optimize its hunting success if it more often encountered prey using these tactics. Alternatively, it is possible that individual variation in learning rates due to time delays between hunting events drove the observed differences in expertise acquisition. For example, in *DBD*, a predator that played 300 matches in the span of six months might forget more critical information (e.g. prey escape patterns or muscle memory) than one that played 300 matches in the span of 6 days. While this has not been formally tested, a greater delay between exposure events is hypothesized to attenuate or even negate the relationship between success and experience [@Endler1991;@Wright.etal2022]. Moreover, the predators could have differed in their ability to detect prey. For instance, it is widely demonstrated that predators learn visual cues such as coloration to recognize and avoid unpalatable prey [@Skelhorn.etal2016;@Ward-Fear.etal2020;@McLellan.etal2021], or habitat characteristics to locate food patches [@Ehlinger1989;@Hughes.etal1992;@Warburton2003]. @Szopa-Comley.etal2020 also found consistent among individual variation in the capacity to detect cryptic and conspicuous prey in three-spined sticklebacks (*Gasterosteus aculeatus*). Thus, predators could differ in their expertise if they do not learn equally how to exploit the visual cues that facilitate prey detection.

@@

*je suis rendu ici pour la correction*
*m'assurer que je nuance bien et que je fais pas ressortir que l'expérience c'est full important*

The predator population displayed an increase in foraging flexibility when reaching the intermediate level of experience. As it reached an advanced level of experience, it returned to a level of flexibility that was similar to novice levels. This is commonly observed in juvenile predators across the animal kingdom, because exploring and learning different tactics at this developmental stage is crucial to become a skillful hunter [@Vehanen2003;@Johnson.Wilbrecht2011;@Thiers.etal2014;@deGrissac.etal2016]. Thus, predators in *DBD* were probably exploring and refining different tactics at this stage of experience. Within the population, differences in individual foraging specialization among predators increased with experience, which was related to the degree of variability in prey encounters. Predators that encountered groups of prey with similar speeds across matches specialized in hunting at high speeds, while those that encountered varying groups of prey adopted a slower and flexible strategy. Fast-paced hunting is indeed a highly specialized tactic suited for prey that use rapid escapes [@Endler1991;@Bro-Jorgensen2013;@Wilson.etal2018], while a slower and flexible tactic can be useful to minimize the consequences of uncertainty when hunting prey that use unpredictable escapes [@Szopa-Comley.Ioannou2022]. This is further supported by the fact that specialist and flexible hunters both achieved similar success throughout the study period. Interestingly, the behavioural response (i.e. tactic use and specialization) to experience by individual predators differed. For instance, 42.7% of the population did not alter their degree of specialization with experience (i.e. remaining either faster and more specialized, or slower and more flexible), while 57.3% of the population displayed a switch from a specialized to a flexible tactic or vice-versa with experience. Thus, our results provide direct evidence that the mechanism underlying the resource-predictability hypothesis may indeed involve predators learning at varying degrees how to specialize on their prey [@Weimerskirch.etal2005;@Weimerskirch2007;@Woo.etal2008;@Phillips.etal2017].

*ici il y a des changements importants à apporter*

As predators gained experience, their tactic was increasingly matched to the speed of their prey. One interpretation could be that both predators and prey learned from each other in an arms-race-like reciprocal relationship [@Kishida.etal2006;@Kishida.etal2009;@Edgell.Rochette2009a;@Mougi.etal2011]. For instance, predators that encountered faster prey could have learned to increase their speed to better capture them, resulting in an increase in the speed of the prey to circumvent the predator's attacks. In this type of system, faster prey should be better at escaping both slower and faster predators [@Mougi.etal2011], which concords with what we previously observed in this sytem [@FraserFranco.etal2022]. @BrodieIII.BrodieJr.1999 argue that when prey express defensive phenotypes (e.g. physical armaments or venom), selection on predators should be strong because the consequences of being injured are greater than missing a meal. If predators improve their exploitative ability, then an arms-race should emerge, and the consequences of hunting dangerous prey should decrease [@BrodieIII.BrodieJr.1999]. Similarly, we found that has the predator gained experience, the negative consequences of encountering prey groups with higher speeds were relaxed, and the variation in success among predators decreased. However, in an arms-race, faster predators would have successfully preyed upon faster and slower prey and would have obtained higher success than slower predators [@Mougi.etal2011], which was not the case in the present study. A more likely scenario is that predators and prey in *DBD* were involved in a matching response relationship [@Mougi.etal2011], because faster-specialist and slower-flexible hunters preyed upon different prey, but they both achieved equal success. Thus predators in *DBD* appear to optimize their success by learning to match their tactic to their prey with experience, suggesting that learning through reciprocal interactions may attenuate selection exerted by prey on predators [@Anderson1995;@Ancel1999;@Borenstein.etal2006;@Paenke.etal2007].

@@

*arranger la conclusion*

Trait-mediated interactions that affect prey capture are the most important processes driving predator-prey dynamics [@abramsEvolutionPredatorPreyInteractions2000]. While most studies assume that predators maximize prey capture by matching their tactic to their prey [@abramsEvolutionPredatorPreyInteractions2000], it has remained largely unknown whether this results from predators learning how to hunt their prey, in part because of the challenges of investigating direct interactions in the wild. By capitalizing on a virtual predator-prey system where interactions were directly monitored, we found that individual predators displayed large differences in the development of their expertise. With experience, half of the predator population changed their behaviour by developping either a specialized or flexible tactic that was matched to the speed of their prey. Overall, both type of hunters achieved equal hunting success. Our results have potential applications for predator-prey models of trait-matching. For instance, simulation studies could incorporate individual variation in experience or learning to better predict under which ecological/evolutionary contexts specialization should be favoured over flexibility. Lastly, virtual systems are increasingly recognized among ecologists as being useful to test hypotheses on consumer-resource interactions [@Barbe.etal2020;@Beauchamp2020;@Cere.etal2021;@FraserFranco.etal2022], but also in other fields such as citizen science and conservation [@Sandbrook.etal2015;@Redpath.etal2018;@Duthie.etal2021]. We therefore hope that our study will inspire more collaborations between scientists and the videogame industry to tackle fundamental questions in ecology.

@@

# Add model column
loo_tab[
  , model := c(
    "prey speed + group-level smoothers",
    "predator xp + prey speed + group-level smoothers",
    "group-level smoothers",
    "predator xp + group-level smoothers",
    "predator xp"
    )
 ]

@@

**Figure 3.** Individual behavioural distribution of the predators' speed drawn from the MDHGLM estimates for individuals that had (A) the greatest increase in specialization and (B) the greatest increase in flexibility. The background (gray) distributions are for when individuals were novice hunters, and the foreground (blue) distributions with solid contour lines are for when they were advanced hunters. Both figure panels are ordered by ascending degree of increase in either specialization or flexibility. We selected the individuals displayed in the figure by first subtracting the estimated standard deviation of all individuals as novices with their standard deviation as advanced hunters, and then selecting those with the greatest difference using the 25% and 75% quantiles. Individuals on panel A have an increase in specialization equal or greater than 0.2 standard deviations, while those on panel B have an increase in flexibility equal or greater than 0.28 standard deviations. *check ici que les pourcentages font du sens*

>>>>

Keywords: foraging behaviour, reciprocal behavioural plasticity, learning, antipredator behaviour, virtual ecology, Dead by Daylight

@@

# Open percentages table
path <- file.path(here::here("outputs", "03_outputs_model-processing"))
percent_tab1 <- data.table(readRDS(file.path(path, "GAMM_percentages.rds")))
percent_tab2 <- data.table(readRDS(file.path(path, "DHMLM_percentages.rds")))
```

Out of all five models, the two that best predicted the data, with very similar expected log pointwise densities (elpd), were the models accounting for the prey group's speed (Table 1). Predators differed substantially in the relationship between hunting success and cumulative experience (i.e. expertise: Figure 1A-B). We found evidence that these differences were in part mediated by prey speed because individuals had distinct patterns after we controlled for the mean speed of the prey groups compared to when we did not (Figure 1A-B). For instance, many individual curves shifted upwards. Precisely, the percentage of individuals that displayed a >0.5 increase in success changed from `r toString(scales::percent(percent_tab1[2,]$percentage, accuracy = 0.1))` to `r toString(scales::percent(percent_tab1[5,]$percentage, accuracy = 0.1))` after we accounted for prey speed (Appendix S1: Figure S1A). In this model (i.e. Figure 1B-C), `r toString(scales::percent(percent_tab1[4,]$percentage, accuracy = 0.1))` of the population showed a >0.5 decrease in success (Appendix S1: Figure S1B), and the remaining `r toString(scales::percent(percent_tab1[6,]$percentage, accuracy = 0.1))` displayed little to no change (between -0.5 and 0.5) in success across experience (Appendix S1: Figure S1C).

@@

Individual predators differed slightly in their average movement speed across experience levels (i.e. predator ID (mean); Figure 2 and Appendix S1: Table S2). However, there was strong evidence that they displayed differences in foraging specialization, with a 0.1 unit increase in standard deviation from novice to advanced, indicating that differences increased slightly (i.e. predator ID (sigma) is higher at the advanced level; Figure 2 and Appendix S1: Table S2). Moreover, some individual predators switched from a flexible to a specialized hunting tactic, and vice-versa, as they gained experience (Figure 3). Importantly, `r toString(scales::percent(percent_tab2[1,]$percentage, accuracy = 1))` of the predator population displayed a large change in foraging specialization/flexibility with experience (i.e. >0.2 change in standard deviation), `r toString(scales::percent(percent_tab2[2,]$percentage, accuracy = 1))` displayed lower changes (i.e. >0.05 and <0.2 change in standard deviation), while `r toString(scales::percent(percent_tab2[3,]$percentage, accuracy = 1))`remained relatively stable (i.e. <0.05 change in standard deviation).

@@

The predator's mean speed and IIV were only weakly negatively correlated with hunting success across experience (Figure 4 and Appendix S4: Table S1), suggesting that slower/flexible and faster/specialist predators were both equally successful. This is further supported in the scatterplot showing no apparent relationship between success and IIV in speed (Appendix S1: Figure S2). However, there was strong evidence that individuals who encountered groups of prey with faster speeds were less successful (Figure 4A-B and Appendix S4: Table S1). Predators also had greater success across the study when encountering more variable groups of prey (Figure 4A-B and Appendix S4: Table S1). Both relationships remained structurally stable across experience (Figure 4-C)

@@

Hunting experience is predicted to increase predator foraging specialization when resources are predictable [@Estes.etal2003;@Tinker.etal2008;@Tinker.etal2009]. However, when resources vary, learning with experience should increase behavioural flexibility [@Stephens1993;@Ishii.Shimada2010;@Mery.Burns2010;@Snell-Rood2013;@Wright.etal2022]. Our results show that there was no directional increase in either behavioural specialization or flexibility with experience at the population level. Instead, individual predators developed their own expertise and behavioural trajectory over successive encounters with the prey. There was a continuum of hunting styles ranging from a slower and flexible strategy to a highly specialized fast-paced strategy. Specialized cursorial hunters encountered similar groups of prey while slower and flexible hunters encountered varying groups of prey, with both achieving similar success over the study period. With experience, predators increasingly matched their foraging specialization to the speed of the prey that they encountered, but they did not achieve greater success, probably because the prey were also matching their speed to the predator. Our observations suggest that predators in *DBD* learn to adjust their foraging specialization, not to the variance, but to the mean behaviour of the prey that they encounter throughout their lifetime in the game.

@@

Empirical research shows that task proficiency often increases nonlinearly with experience and stabilizes at an expert level [reviewed in @Dukas2019]. Our analyses revealed a similar trend, with a 13% population increase in success when predators became advanced hunters. However, because the game pairs players with similar skill, the increase in expertise could have potentially been greater if predators and prey were paired randomly. Individual predators in *DBD* also displayed distinct patterns of expertise acquisition. We predicted that this would occur if, by chance, predators differed in the prey that they encountered, because some may be easier and others more difficult to capture. In nature, prey can use a variety of defenses such as physical armaments, toxins, camouflage, or antipredator behaviours to escape predation [@BrodieIII.BrodieJr.1999;@Bowen.etal2002;@brodieCoEvolutionPredatorsPrey2010;@Nomura.etal2011;@Carey.Wahl2011]. In *DBD* we previously showed that faster movement is an effective strategy used by the prey to avoid predation [@FraserFranco.etal2022], and other studies have found that as well [@Walker.etal2005;@Kelley.Magurran2011;@Martin.etal2022]. Our results confirm that prey speed influenced expertise acquisition at the individual level to some extent. This is not surprising because capturing faster prey requires costly and specialized cognitive abilities and coordination [@Kelley.Magurran2011].

However, there were still important differences in expertise acquisition, which suggests that other antipredator tactics may also be involved. For example, a well known antipredator tactic associated with speed that confuses human and non-human predators during the attack sequence is unpredictable escapes [@Jones.etal2011;@Herbert-Read.etal2017;@Moore.etal2017;@Richardson.etal2018]. This tactic compromises the predator's ability to anticipate prey escape routes, but they can adjust to it by using slower approaches before attacking [@Szopa-Comley.Ioannou2022]. Yet, because unpredictability exploits the predator's cognition, slow learners could struggle to optimize their success if they often encounter prey using this tactic which is also extensively used in *DBD* (personal observation).

Alternatively, it is possible that individual variation in learning rates due to time delays between hunting events drove the observed differences in expertise acquisition. For example, in *DBD*, a predator that played 300 matches in the span of six months might forget more critical information (e.g. prey escape patterns or muscle memory) than one that played 300 matches in the span of 6 days. While this has not been formally tested, a greater delay between exposure events is hypothesized to attenuate or even negate the relationship between success and experience [@Endler1991;@Wright.etal2022]. Moreover, the predators could have differed in their ability to detect prey. For instance, nonhuman predators can learn visual cues such as coloration to recognize and avoid unpalatable prey [@Skelhorn.etal2016;@Ward-Fear.etal2020;@McLellan.etal2021], or habitat characteristics to locate food patches [@Ehlinger1989;@Hughes.etal1992;@Warburton2003]. @Szopa-Comley.etal2020 also found consistent among individual variation in the capacity to detect cryptic and conspicuous prey in three-spined sticklebacks (*Gasterosteus aculeatus*). Thus, predators could differ in their expertise if they do not learn equally how to exploit the visual cues that facilitate prey detection.

@@

There were only weak differences among predators in tactic use (i.e. mean speed), but differences in specialization were important and related to how different were the groups of prey that they encountered. Predators that encountered groups of prey with similar speeds across matches specialized in hunting at high speeds, while those that encountered varying groups of prey adopted a slower and flexible strategy. Fast-paced hunting is indeed a highly specialized tactic suited for prey that use rapid escapes [@Endler1991;@Bro-Jorgensen2013;@Wilson.etal2018], while a slower and flexible tactic can be useful to minimize the consequences of uncertainty when hunting prey that use unpredictable escapes [@Szopa-Comley.Ioannou2022]. However, it remains uncertain whether this phenotypic matching enables predators with different degrees of specialization to achieve equal success within populations [@Woo.etal2008]. Here, we found that all hunters along the flexible-specialist continuum achieved similar success throughout the study period (Appendix S1: Figure S2). Thus, our results provide direct evidence that predators matching their tactic to their prey may be key in maintaining behavioural diversification in predator-prey systems.

Surprisingly, the effect of experience on foraging behaviour was much more subtle than we expected. For instance, the predator population maintained their speed and degree of specialization throughout the study period, and individual differences in mean speed did not change with experience. However, differences among predators in foraging specialisation did increase slightly with experience, with some individuals becoming increasingly flexible. Interestingly, the behavioural response (i.e. specialization) to experience by individual predators differed. For instance, 44% of the population did not alter their degree of specialization with experience (i.e. remaining either faster and more specialized, or slower and more flexible), while 56% of the population displayed a switch from a specialized to a flexible tactic or vice-versa with experience. These changes were accompanied by predators increasingly matching their specialization to the mean speed of the prey groups across experience, instead of the variability between encounters. This suggests that it may be easier for predators to specialize on their prey by relying on mean cues (i.e. mean behaviour) instead of relying solely on resource heterogeneity [@Weimerskirch.etal2005;@Weimerskirch2007;@Woo.etal2008;@Phillips.etal2017].

It is likely that predators were also driving changes in prey behaviour because most predator-prey behavioural relationships remained stable even though half of the population switched from a specialist to a flexible strategy and vice-versa across experience. This implies that the prey were probably also learning how to avoid predation through repeated interactions. Our results concord with what @Mougi.etal2011 define as a matching response relationship, because faster-specialist and slower-flexible hunters preyed upon different prey, but they both achieved equal success. These types of reciprocal responses to interactions have been observed in other predator-prey systems [@Kishida.etal2006;@Kishida.etal2009;@Edgell.Rochette2009a;@McGhee.etal2013], but their broader consequences remain unclear. Assuming that prey also learned during the interaction, which has been shown across many taxa [refs], we can deduce that learning from reciprocal interactions may contribute in stabilizing predator-prey systems, similar to Red Queen dynamics [@brockhurst2014].

While experience did not alter most of the interaction, predators still managed to increase foraging specialization with increasing prey speed across experience, while individual differences in hunting success simultaneously decreased. When prey express defensive phenotypes such as high speeds, selection on predators should be strong because of the consequences of repeated failures. If predators improve their exploitative ability, then the consequences of hunting these prey should decrease [@BrodieIII.BrodieJr.1999]. Similarly, theoretical studies predict that learning may attenuate selection [@Anderson1995;@Ancel1999;@Borenstein.etal2006;@Paenke.etal2007], but failing to account for reciprocal interactions may mask more complex outcomes. Here, learning appears to have reduced differences in success among predators, but success remained lower when predators hunted faster prey. Again, if prey learned how to avoid the predators, then this would explain why advanced hunters still struggled to achieve similar success against faster prey compared to slower prey. Thus, disentanling the consequences of learning from reciprocal interactions may reveal important insights on predator-prey interactions.

@@

Trait-mediated interactions that affect prey capture are the most important processes driving predator-prey dynamics [@abramsEvolutionPredatorPreyInteractions2000]. While most studies assume that predators maximize success by matching their tactic to their prey [@abramsEvolutionPredatorPreyInteractions2000], it has remained largely unknown whether this results from predators learning how to hunt their prey, in part because of the challenges of investigating direct interactions in the wild. By capitalizing on a virtual predator-prey system where interactions were directly monitored, we found that individual predators displayed large differences in the development of their expertise. With experience, the population became increasingly distinct along a flexible-specialist continuum, while interactions remained largely stable. Overall, all hunters achieved similar hunting success. Our results have potential applications for predator-prey models of trait-matching. For instance, simulation studies could incorporate individual variation in experience or learning to better predict under which ecological/evolutionary contexts specialization should be favoured over flexibility. Lastly, virtual systems are increasingly recognized among ecologists as being useful to test hypotheses on consumer-resource interactions [@Barbe.etal2020;@Beauchamp2020;@Cere.etal2021;@FraserFranco.etal2022], but also in other fields such as citizen science and conservation [@Sandbrook.etal2015;@Redpath.etal2018;@Duthie.etal2021]. We therefore hope that our study will inspire more collaborations between scientists and the videogame industry to tackle fundamental questions in ecology.

@@

# Add model column
loo_tab[
  , model := c(
    "predator xp + group-level smoothers + prey speed",
    "group-level smoothers + prey speed",
    "group-level smoothers",
    "predator xp + group-level smoothers",
    "predator xp"
    )
 ]

@@

**Figure 3.** Individual behavioural distribution of the predators' speed drawn from the MDHGLM estimates for individuals that had (A) the greatest increase in specialization and (B) the greatest increase in flexibility. The background (gray) distributions are for when individuals were novice hunters, and the foreground (blue) distributions with solid contour lines are for when they were advanced hunters. Both figure panels are ordered by ascending degree of increase in either specialization or flexibility. We selected the individuals displayed in the figure by first subtracting the estimated standard deviation of all individuals as novices with their standard deviation as advanced hunters, and then selecting those with the greatest difference using the 25% and 75% quantiles. Individuals on panel A have an increase in specialization equal or greater than 0.2 standard deviations, while those on panel B have an increase in flexibility equal or greater than 0.27 standard deviations.
